%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{System Engineer} % Job title
{Texas Instruments} % Organization
{Dallas, TX} % Location
{Sep. 2019 - PRESENT} % Date(s)
{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Designed and evaluated performance of efficient neural networks with low-bit (binary), sparse, and quantized models.}
			\item {Benchmarked state-of-art machine learning algorithms for vision and speech tasks using TensorFlow and PyTorch.}
			\item {Provided support to internal digital design teams (RTL coding) and external customers for machine learning model design and deployment on embedded systems.}
			\item {Trained summer intern and other team members for cross-functional projects.}
			\item {Built deep learning training infrastructure using Docker, Conda, and Git on internal servers and AWS cloud servers.}
		\end{cvitems}
}

\cventry
{Research Intern} % Job title
{} % Organization
{} % Location
{May. 2018 - July. 2018} % Date(s)
{
		\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Designed and tested efficient neural networks for embedded devices.}
				\item {Prototyped novel quantization scheme for low-bit fixed-point arethmetics.}
				\item {Implemented and benchmark convolutional neural network (CNN) performance for vision tasks.}
		\end{cvitems}
}

%---------------------------------------------------------
	\cventry
		{Research Assistant} % Job title
		{Georgia Institute of Technology} % Organization
		{Atlanta, GA} % Location
		{Sep. 2014 - Aug. 2019} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Led the development and deployment of machine learning models on large-scale datasets from data acquisition to web services.}
				\item {Advised junior Ph.D. and Master students in interdisciplinary research.}
				\item {Developed and provided customer support to sponsors for open-sourced and proprietary research softwares.}
				% \item {Developed and support in-house numerical (FD) simulation tools for elastic wave propagation in complex medium.}
				\item {Maintained HPC server and optimized for storage and processing of large-scale datasets.}
			\end{cvitems}
		}


%---------------------------------------------------------
	\cventry
		{Research Intern} % Job title
		{Houston Research Center, Aramco Service Company} % Organization
		{Houston, TX} % Location
		{Aug. 2015 - Nov. 2015} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Preapared and organized large-scale seismic datasets from land acquisition for machine learning models.}
				\item {Processed land acquisition data searching for small events in the noisy environment.}
				\item {Designed and evaluated machine learning algorithms for dimension reduction, image segmentation and object tracking.}
%				 \item {Built tools to enhance signal quality and cancel noise using dictionary learning backed algorithms.}
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{Research Intern} % Job title
		{Microsoft Research} % Organization
		{Redmond, WA} % Location
		{May. 2014 - Aug. 2014} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Developed numerical simulation software for ultrasonic wave propagation in \textit{C++} with a \textit{MATLAB} interface.}
				\item {Conducted acoustic measurements in anechoic chamber testing prototype products.}
				\item {Published and presented results in research paper and conferences.}
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{Research Co-op} % Job title
		{Bose Coporation} % Organization
		{Framingham, MA} % Location
		{Jan. - May., Aug. - Dec. 2012} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Worked with marketing team in identifying customer's requirements and make product definition.}
%				 \item {Worked with transducer team to designed and simulated transducer array using their newly developed waveguide and subwoofer.}
%				 \item {Built prototype speaker system on wood frame and developed noise reduction circuit for power amplifier.}
%				 \item {Measured and evaluated acoustic system in both anechoic chamber and living room setup (both objective and subject evaluations).}
				\item {Led the product prototyping in early stage and make demonstration to executives.}
%				 \item {Design went into development and eventually became a mass market product.}
				\item {Developed and maintained \textit{MATLAB} and \textit{Perl} script to automate testing procedure.}
				%\item {Assisted adaptive microphone array design for conference setup.}
			\end{cvitems}
		}

%---------------------------------------------------------
\end{cventries}
